### 2018-08-29 scripts/02-metrics/01-metric_characterisation/README.Rmd
add ability to link to results

# Metric conformity

@@

Differences between two datasets should be reflected in certain changes in the metrics. This can be formalised in a set of rules, for example:

* If the position of some cells are different than in the gold standard, the score should decrease.
* If the topology of the network is different than that in the gold standard, the score should not be perfect.
* The more cells are filtered from the trajectory, the more the score should decrease.

Here, we assess whether metrics conforms such rules empirically:

@@

>>>>

# Metric characterisation

@@

A first characterisation of the metrics. For each metric we:

- generate some examples to get some intuition on how the metric works
- test the robustness to a metric to stochasticity or parameters when appropriate

@@

The results of this experiment are available [here](`r link_to_results()`)
